Efficient pedigree recording for fast population genetics simulation

### 2017-12-29 forwards_paper.tex
oops--y axis same here

The peak RAM use in gigabytes (GB) is shown for the simulations with selection in Figure~\ref{sfig:ramsel} aand for the
simulations without selection in Figure~\ref{sfig:ramnosel}.  For our parameters, which involved simplifying every
$10^3$ generations,  pedigree tracking requires more RAM.  With \fwdpy{}/\fwdpp{}, the reason for the extran RAM use is clear.  When pedigree tracking, a non-recombinant
individual still requires one new edge and two new nodes to be allocated.  Without pedigree tracking, no new memory is
allocated for such an offspring.  Thus, pedigree tracking accumulates a large amount of data in RAM until
simplification.  This extra RAM consumption is the trade off for reduced run times and the degree of extram RAM needed
can be reduced by simplifying more often.  The simulations where we run the simplification step in a separate thread
require even more RAM (dashed line in Figure \ref{sfig:ramsel}) because up to four sets of unsimplified data are
stored in RAM.  In practice, the RAM consumption can be minimized by simplifying more often.

@@

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}. Note that the y-axis scales differ considerably across panels.}
\end{figure}
\end{document}

>>>>

The peak RAM use in gigabytes (GB) is shown for the simulations with selection in Figure~\ref{sfig:ramsel} and for the
simulations without selection in Figure~\ref{sfig:ramnosel}.  For our parameters, which involved simplifying every
$10^3$ generations,  pedigree tracking requires more RAM.  With \fwdpy{}/\fwdpp{}, the reason for the extra RAM use is clear.  When pedigree tracking, a non-recombinant
individual still requires one new edge and two new nodes to be allocated.  Without pedigree tracking, no new memory is
allocated for such an offspring.  Thus, pedigree tracking accumulates a large amount of data in RAM until
simplification.  This extra RAM consumption is the trade off for reduced run times and the degree of extra RAM needed
can be reduced by simplifying more often.  The simulations where we run the simplification step in a separate thread
require even more RAM (dashed line in Figure \ref{sfig:ramsel}) because up to four sets of unsimplified data are
stored in RAM.  In practice, the RAM consumption can be minimized by simplifying more often.

@@

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}.}
\end{figure}
\end{document}
